Meta-analysis

### 2019-08-05 03_Preliminary_analysis.Rmd
updating preliminary analysis. Removing multiple variations of sulphur treatments

@@

```{r echo = FALSE, message=FALSE, warning=FALSE}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

@@

#### Effect of Fungicide 
**on proportional yield gain with repect to time of application**
##### Tebeconazole
```{r}
PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>% # remove any fungicide groups with less than 5 observations
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

@@

>>>>

# Rewrite all variations of sulphur treatments as just sulphur
PM_MB_means$Fungicide[PM_MB_means$Fungicide == "Sulphur"| PM_MB_means$Fungicide == "Sulphur (SC)" | PM_MB_means$Fungicide == "Sulphur (Ultra SC)" | PM_MB_means$Fungicide == "Sulphur (WP)"] <- "Sulphur"
```

```{r row_spacing}

@@

#### Effect of Fungicide 
**on proportional yield gain with repect to time of application**
First lets look at the quantiles for each fungicide irrespective of other factors.
We will focus on proportional yield gain, compared to no treatment control, as this should partially correct for some spatial and seasonal effects.  
```{r}
PM_MB_means %>%
   group_by(Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

# plot table as a density plot

ggplot(PM_MB_means, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first Sulphur fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r}

@@

```{r echo = FALSE, message=FALSE, warning=FALSE}
PM_MB_means %>%
   filter(Fungicide != "control") %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(
      as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") -
         as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))
